Understanding the impacts of video-guided activities on parent-child interaction

### 2021-01-11 paper/manuscript.tex
ready to submit

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Understanding the impacts of video-guided activities on parent-child interaction},
            pdfauthor={George Kachergis, Emily Hembacher, Veronica Cristiano, Hanwen Vivian Zhang, \& Michael C. Frank},
            pdfkeywords={digital parenting advice; joint attention; lexical diversity; guided play},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\shorttitle{Impacts of videos on parent-child interaction}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Gallaudet University\\\textsuperscript{3} Cornell University}
\keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 4995}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\usepackage{lineno}

\linenumbers
\usepackage{float}

@@

Correspondence concerning this article should be addressed to Michael C. Frank, Stanford, CA 94305 USA. E-mail: \href{mailto:mcfrank@stanford.edu}{\nolinkurl{mcfrank@stanford.edu}}}

\abstract{
Early parenting practices play an important role in shaping the future outcomes of young children (Hart \& Risley, 1995; Heckman, 2006).
In particular, high-quality early interactions and language input appear to facilitate language learning and result in higher levels of school performance.
The rise of phone-based parenting applications (``apps'') holds the promise of delivering low-cost, positive interventions on parenting style to a wide variety of populations.
Of special interest are the parents of very young children, who are often difficult to reach in other ways. Yet little is known about the effects of communicating to parents through app-based interventions.
We showed parents short videos depicting age-appropriate parent-child activities from a commercial parenting app, and found that the quality of parent-child interactions increased in some ways as a result of the intervention.
Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.

@@

@@

The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes (Cartmill et al., 2013; Hart \& Risley, 1995; Hirsh-Pasek et al., 2015; Marchman \& Fernald, 2008; see Schwab \& Lew-Williams, 2016 for a review). Thus, because of the potential for large downstream effects (Heckman, 2006), there is tremendous interest in interventions that change children's language environment.
And because parents define a large portion of that environment, especially before the onset of formal schooling, parent behavior is a critical locus for such interventions.
Many effective parenting interventions require large resource investments and require many hours of in-person contact (Gertler et al., 2014; Leung, Hernandez, \& Suskind, 2018; Schweinhart et al., 2004), making implementation at scale a daunting proposition.
For this reason, many researchers targeting early language are interested in delivering parenting interventions remotely -- through texts, apps, and videos delivered on digital devices.
But what do parents take away from these short messages about what to do with or how to talk with their children?

The content provided by digital parenting interventions runs the gamut from general parenting messages and facts from child development research to specific advice and suggested activities.
A growing body of evidence suggests that these digital interventions can be effective across a range of cultures, income levels, and children's ages (for a review, see Breitenstein, Gross, \& Christophersen, 2014).
For example, in contrast to a face-to-face parent training intervention, a tablet-based version saw significantly higher session completion rates (51\% attendance vs.~85\% module completion) and comparable or larger effect sizes on parents' and children's (aged 2 to 5 years) behavior (Breitenstein, Fogg, Ocampo, Acosta, \& Gross, 2016).
Often, however, the theory of change presupposed by such interventions is relatively vague.
Both within and outside the realm of academic interventions, messages to parents of young children often seek to provide knowledge about some aspect of development (e.g., early language), often in tandem with a suggestion regarding activities.
Such messages are assumed to inform parents' choice of behaviors, spurring them to engage in some target activity, which is assumed to be more stimulating than what parents would have done otherwise.

This theory of change is typically grounded in ideas about guided play and early language stimulation.
Child-directed speech varies not only in quantity (i.e., the number of total tokens), but also in quality in terms of the diversity of the tokens (Malvern, Richards, Chipere, \& Durán, 2004) or the context-appropriateness of the speech (Cartmill et al., 2013), both of which have been linked to children's subsequent language development.
Further, language learning---especially the acquisition of early vocabulary in the first years---appears to be supported preferentially by parents and children \emph{jointly attending} to some object or activity (Baldwin, 1991; Bigelow, MacLean, \& Proctor, 2004).
Episodes of joint attention are frequent during guided play, when parents set goals and scaffold their child's activities (Weisberg, Hirsh-Pasek, \& Golinkoff, 2013; Wood, Bruner, \& Ross, 1976).
Thus, the current literature supports interventions that encourage parents to provide high-quality language and interaction through something like guided play---whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.

But is this theory of change correct? That is, does the provision of knowledge and activities lead to higher-quality play?
Alternatively, by focusing parents on a specific activity, this approach could be flawed, causing parents to over-focus on achieving the superficial goals of the activity.
This problem might be especially likely with video messages, which could encourage parents to try to mimic a model's specific speech and/or actions.
Attempting to reproduce such surface details of a video-guided activity could in turn result in less high-quality talk, with less responsiveness to their child's play.
Another possibility is that these messages might produce the desired effect, but only for those parents who already have a general orientation towards children's early learning.

Our current experiments were designed to make a direct test of this question: How do parents change their interactions with young children on the basis of short video parenting messages?
In two experiments, we collected data from parent-child dyads in a local children's museum.
We showed parents in the experimental group a single short video modeling an interactive toy-based activity along with a scientific justification.
Parents in the control group received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2).
We then gave the toys from the video to all dyads and videotaped their interactions, coding for caregivers' language quantity and quality as well as joint attention.

@@

In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
Parents were randomly assigned to one of two conditions: parents in the \emph{Activity Video} condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
Parents in the \emph{No Video} condition did not watch an activity video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.

@@

\hypertarget{participants.}{%
\subsubsection{Participants.}\label{participants.}}

60 infants (F = 43, M = 17) aged 6-24 months (19 6-11.9 month-olds: 9 in the control condition, 10 in Activity Video; 20 12-17.9 month-olds: 11 control, 9 Activity Video; 21 18-24 month-olds: 10 control, 11 Activity Video) and their parents participated in a museum in northern California.
We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
62\% of participants (n = 37) had been exposed to two or more languages, as indicated by their parent.
Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5).
Fifteen parents reported that their child was of Hispanic origin.
Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = 5), some college (n = 7), four-year college (n = 16), some graduate school (n = 2), to completed graduate school (n = 30).

\hypertarget{materials.}{%
\subsubsection{Materials.}\label{materials.}}

@@

Participants were randomly assigned to either the \emph{Activity Video} condition or the \emph{No Video} condition.
Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
The two conditions were yoked: for each Activity Video participant who saw a particular video and received the associated props, a participant in the No Video condition received the same props to use without seeing the video.
Parents also completed the Early Parenting Attitudes Questionnaire (EPAQ; Hembacher \& Frank, 2020).
The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (see SI).

\hypertarget{procedure.}{%
\subsubsection{Procedure.}\label{procedure.}}

@@

In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless Shure lavalier microphone to record their child-directed speech.
After three minutes of play had elapsed, parents were told they could stop playing and the cameras and microphone were turned off.
Parents were then asked to complete the EPAQ before being debriefed.

\hypertarget{joint-attention-coding-procedure.}{%
\subsubsection{Joint Attention Coding Procedure.}\label{joint-attention-coding-procedure.}}

The video of each session was manually coded for episodes of joint attention (JA) using the Datavyu software (Team, 2014).
The video taken at floor level was coded by default, but the other video was referred to if the participants were occluded or if there was technical difficulty with the first camera.
Each session's video was coded for episodes of coordinated JA, episodes of passive JA, and parental bids for JA.
Parental bids for JA were defined as any attempt to initiate joint attention (i.e labeling, pointing, or otherwise drawing attention to an object) that did not result in passive or coordinated JA.
If more than 3 seconds elapsed between bids, they were coded as separate attempts.
An episode of joint attention was considered \emph{passive} if both participants visually focused on an object for 3 or more seconds but the child did not acknowledge the parent.
If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same episode of joint attention.
A joint attention episode was considered \emph{coordinated} if both participants visually focused on an object for 3 or more seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent such as looking at their face, gesturing, vocalizing, or turn-taking.
Full details of our guidelines for coding joint attention are available in SI.

@@

Parents' child-directed speech during the play sessions (mean duration: 3.25 min) was transcribed; child utterances were not considered.
Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2\footnote{Preregistration: \href{https://osf.io/2bpdf}{https://osf.io/2bpdf/}}, with any deviations or exploratory analyses noted.
Below we first report the lexical diversity results, followed by the joint attention results.

@@

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), the child's sex, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
These models included random intercepts per video.
Of these exploratory regressions, two showed notable effects involving the EPAQ subscales, and one other showed an effect of the child's sex.
First, in the word types regression, parents with higher Affection and Attachment scores used more word types per minute after watching an Activity Video (interaction of condition and AA: \(\beta=6.81\), 89\% CI = {[}0.87, 13.13{]}, \emph{pd} = 0.97).
Second, in the regression examining the rate of passive JA episodes, parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=-0.34\), 89\% CI = {[}-0.62, -0.07{]}, \emph{pd} = 0.98).
However, after an Activity Video, higher RR parents did not show this decrease in passive JA (interaction of condition and RR: \(\beta=0.63\), 89\% CI = {[}0.23, 1.03{]}, \emph{pd} = 0.99).
Parents with higher education also showed a lower rate of passive JA episodes (\(\beta=-0.25\), 89\% CI = {[}-0.45, -0.04{]}, \emph{pd} = 0.97).
Finally, parents with male children made bids for JA at a higher rate (mean: 2.76 bids/min) than those with female children (mean: 2.49, \(\beta=0.82\), 89\% CI = {[}0.06, 1.54{]}, \emph{pd} = 0.96).

To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
Words that were strongly indicative of being from the Activity Video condition include \enquote{give}, \enquote{big}, \enquote{small}, \enquote{ribbit}, \enquote{thank}, \enquote{have}, and \enquote{bus}, while words that were most characteristic of the No Video condition include \enquote{shake}, \enquote{ready}, \enquote{oh}, \enquote{on}, \enquote{going}, \enquote{going}, \enquote{see}, \enquote{let}, and the child's name.

@@

Experiment 1 found that parents who watched an activity video made more bids for joint attention and spoke more words tokens per minute to their children, but had lower lexical diversity compared to parents who played with their children as they normally would at home.
Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
Experiment 2 focuses on replicating the key findings using a stronger control group, as well as a restricted number of preregistered predictions.\footnote{Preregistration: \href{https://osf.io/2bpdf}{https://osf.io/2bpdf/}.}

@@

\hypertarget{participants.-1}{%
\subsubsection{Participants.}\label{participants.-1}}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Understanding the impacts of video-guided activities on parent-child interaction},
  pdfauthor={George Kachergis1, Emily Hembacher1, Veronica Cristiano2, Hanwen Vivian Zhang3, \& Michael C. Frank1},
  pdflang={en-EN},
  pdfkeywords={language development; parent intervention; childhood development; joint attention; lexical diversity},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Impacts of videos on parent-child interaction}
\keywords{language development; parent intervention; childhood development; joint attention; lexical diversity\newline\indent Word count: 6279}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{float}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

@@

The data that support the findings of this study are openly available in OSF at \url{http://doi.org/10.17605/OSF.IO/2BPDF}

Correspondence concerning this article should be addressed to George Kachergis, Stanford, CA 94305 USA. E-mail: \href{mailto:kachergis@stanford.edu}{\nolinkurl{kachergis@stanford.edu}}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Gallaudet University\\\textsuperscript{3} Cornell University}

\abstract{
Early parenting practices play an important role in shaping children's future outcomes.
In particular, high-quality early interactions can facilitate language learning and school performance.
The rise of phone-based parenting applications (``apps'') could deliver low-cost interventions on parenting style to a wide variety of populations, especially the parents of very young children, who are often difficult to reach in other ways.
Yet relatively little is known about the local effects of communicating to parents about how they should interact via videos.
In two studies (one preregistered), we investigated effects of short videos on parent behavior.
We showed parents videos depicting age-appropriate parent-child activities from a parenting app.
We found that after watching the video, parents spoke more and made more bids for joint attention, as compared with controls who watched no video (experiment 1; N=60) or a science video (experiment 2; N=84).
These results suggest that activity videos can lead to local changes in parent engagement, providing support for the use of such videos as a part of broader app-based parenting interventions.
}

@@

The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes (Cartmill et al., 2013; Hart \& Risley, 1995; Hirsh-Pasek et al., 2015; Marchman \& Fernald, 2008; Rowe, 2012; see Schwab \& Lew-Williams, 2016 for a review).
Thus, because of the potential for large downstream effects (Heckman, 2006), there is tremendous interest in interventions that change children's language environment.
And because parents define a large portion of that environment, especially before the onset of formal schooling, parent behavior is a critical locus for such interventions.
Many effective parenting interventions require large resource investments and require many hours of in-person contact (Gertler et al., 2014; Leung, Hernandez, \& Suskind, 2018; Schweinhart et al., 2004), making implementation at scale a daunting proposition.
For this reason, many researchers targeting early language are interested in delivering parenting interventions remotely -- through texts, apps, and videos delivered on digital devices.
But what do parents take away from these short messages about what to do with or how to talk with their children?
In this paper, rather than conducting a large-scale intervention, we investigate the ways that parents change their local behavior with children immediately after seeing a short video instructing them on an activity, investigating one of the building blocks of many larger interventions.

The content provided by digital parenting interventions runs the gamut from general parenting messages and facts from child development research to specific advice, coaching, and suggested activities.
A growing body of evidence suggests that these digital interventions can be effective across a range of cultures, income levels, and children's ages (for a review, see Breitenstein, Gross, \& Christophersen, 2014).
For example, in contrast to a face-to-face parent training intervention, a tablet-based version saw significantly higher session completion rates (51\% attendance vs.~85\% module completion) and comparable or larger effect sizes on parents' and children's (aged 2 to 5 years) behavior (Breitenstein, Fogg, Ocampo, Acosta, \& Gross, 2016).
Often, however, the theory of change presupposed by such interventions is relatively vague.
Both within and outside the realm of academic interventions, messages to parents of young children often seek to provide knowledge about some aspect of development (e.g., early language; Kruythoff-Broekman, Wiefferink, Rieffe, and Uilenburg (2019)), often in tandem with a suggestion regarding activities (e.g., book reading; for a review see Reese, Sparks, and Leyva (2010)).
Such messages are assumed to inform parents' choice of behaviors, spurring them to engage in some target activity, which in turn is assumed to be more stimulating than what parents would have done otherwise.

This theory of change is typically grounded in ideas about guided play and early language stimulation.
Child-directed speech varies not only in quantity (i.e., the number of total tokens), but also in quality in terms of the diversity of the tokens (Malvern, Richards, Chipere, \& Durán, 2004) or the context-appropriateness of the speech (Cartmill et al., 2013), both of which have been linked to children's subsequent language development.
Further, language learning---especially the acquisition of early vocabulary in the first years---appears to be supported preferentially by parents and children \emph{jointly attending} to some object or activity (Baldwin, 1991; Bigelow, MacLean, \& Proctor, 2004).
Episodes of joint attention are frequent during guided play, when parents set goals (e.g., building a tower) and scaffold their child's activities (Weisberg, Hirsh-Pasek, \& Golinkoff, 2013; Wood, Bruner, \& Ross, 1976).
Thus, the current literature supports interventions that encourage parents to provide high-quality language and interaction through something like guided play---whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.

But is this theory of change correct in the case of digital parenting interventions?
That is, does the provision of knowledge and activities via short videos or messages actually lead to higher-quality play?
Alternatively, this approach could be flawed.
For example, focusing parents on a specific activity could cause them parents to over-focus on achieving the superficial goals of the activity while neglecting the broader goals of fostering more -- and more responsive -- interaction.
This problem might be especially likely with video messages, which could encourage parents to try to mimic a model's specific speech and/or actions.
Attempting to reproduce the surface details of a video-guided activity could in turn result in less high-quality talk, with less responsiveness to their child's play, a target of parent responsiveness interventions (e.g., Landry, Smith, Swank, \& Guttentag, 2008).
(Speaking as a parent, one author of the current paper has found himself occasionally so engrossed in attempting to execute an activity with his children that he has lost track of whether the children are continuing to enjoy it!).

Thus, our goal was to gather information about whether the use of short video parenting messages as a component of broader interventions is supported by their local effects on parent-child interaction and language use.
Our current studies were designed to assess how parents change their interactions with young children on the basis of these videos.\\
We made a first step towards assessing this question by performing two studies within the context of a convenience sample of parent-child dyads in a local children's museum.
We showed parents in the experimental group a single short video modeling an interactive toy-based activity along with a scientific justification.
Parents in the control group received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2).
We then gave the toys from the video to all dyads and videotaped their interactions, coding for caregivers' language quantity and quality as well as joint attention.

@@

In Experiment 1, we invited parents of 6- to 24-month-old infants visiting {[}a children's museum in XXXX{]} to complete video-guided activities from a commercial parenting app that delivers digital parenting advice in the form of short videos.
Parents were randomly assigned to one of two conditions: parents in the \emph{Activity Video} condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
Parents in the \emph{No Video} condition did not watch an activity video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.

@@

\hypertarget{participants}{%
\subsubsection{Participants}\label{participants}}

60 infants (F = 43, M = 17) aged 6-24 months (19 6-11.9 month-olds: 9 in the control condition, 10 in Activity Video; 20 12-17.9 month-olds: 11 control, 9 Activity Video; 21 18-24 month-olds: 10 control, 11 Activity Video) and their parents participated in a museum in {[}XXXX{]}.
We included infants who were exposed to English more than 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
62\% of participants (n = 37) had been exposed to two or more languages, as indicated by their parent.
Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5).
Fifteen parents reported that their child was of Hispanic origin.
Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = 5), some college (n = 7), four-year college (n = 16), some graduate school (n = 2), to completed graduate school (n = 30).

\hypertarget{materials}{%
\subsubsection{Materials}\label{materials}}

@@

Without their knowledge, participants were randomly assigned to either the \emph{Activity Video} condition or the \emph{No Video} condition.
Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
The two conditions were yoked: for each Activity Video participant who saw a particular video and received the associated props, a participant in the No Video condition received the same props to use without seeing the video.
Parents also completed the Early Parenting Attitudes Questionnaire (EPAQ; Hembacher \& Frank, 2020).
The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (\href{XXXX}{see SI}).

\hypertarget{procedure}{%
\subsubsection{Procedure}\label{procedure}}

@@

In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless Shure lavalier microphone to record their child-directed speech.
After three minutes of play had elapsed, parents were told they could stop playing and the cameras and microphone were turned off.
Parents were then asked to complete the EPAQ before being debriefed.
No compensation was provided to the parents; children were given a sticker of their choice.

Experimenters were aware of the condition structure of the experiment and condition assignment of parents but made no comments or other intervention once the parent-child interaction began.

\hypertarget{joint-attention-coding-procedure}{%
\subsubsection{Joint Attention Coding Procedure}\label{joint-attention-coding-procedure}}

The video of each session was manually coded for episodes of joint attention (JA) using the Datavyu software (Team, 2014), and coders were blind to condition.
The video taken at floor level was coded by default, but the other video was referred to if the participants were occluded or if there was technical difficulty with the first camera.
Each session's video was coded for episodes of coordinated JA, episodes of passive JA, and parental bids for JA.
Parental bids for JA were defined as any attempt to initiate joint attention (i.e labeling, pointing, or otherwise drawing attention to an object) that did not result in passive or coordinated JA.
If more than 3 seconds elapsed between bids, they were coded as separate attempts.
An episode of joint attention was considered \emph{passive} if both participants visually focused on an object for 3 or more seconds but the child did not acknowledge the parent.
If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same episode of joint attention.
A joint attention episode was considered \emph{coordinated} if both participants visually focused on an object for 3 or more seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent such as looking at their face, gesturing, vocalizing, or turn-taking.
Full details of our guidelines for coding joint attention are available in SI.

@@

Parents' child-directed speech during the play sessions (mean duration: 3.25 min) was transcribed; child utterances were not considered.
Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2\footnote{{[}XXXX{]}}, with any deviations or exploratory analyses noted.
Below we first report the lexical diversity results, followed by the joint attention results.

@@

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), the child's sex, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
These models included random intercepts per video.
Of these exploratory regressions, two showed notable effects involving the EPAQ subscales, and one other showed an effect of the child's sex.
First, in the word types regression, parents with higher Affection and Attachment scores used more word types per minute after watching an Activity Video (interaction of condition and AA: \(\beta=6.85\), 89\% CI = {[}0.74, 12.91{]}, \emph{pd} = 0.96).
Second, in the regression examining the rate of passive JA episodes, parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=-0.35\), 89\% CI = {[}-0.63, -0.06{]}, \emph{pd} = 0.97).
However, after an Activity Video, higher RR parents did not show this decrease in passive JA (interaction of condition and RR: \(\beta=0.63\), 89\% CI = {[}0.22, 1.03{]}, \emph{pd} = 0.99).
Parents with higher education also showed a lower rate of passive JA episodes (\(\beta=-0.25\), 89\% CI = {[}-0.46, -0.05{]}, \emph{pd} = 0.97).
Finally, parents with male children made bids for JA at a higher rate (mean: 2.76 bids/min) than those with female children (mean: 2.49, \(\beta=0.81\), 89\% CI = {[}0.07, 1.57{]}, \emph{pd} = 0.96).

To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (\href{https://osf.io/2bpdf/files/github/language_analyses/Exp1_characteristic_chart.html}{see SI} for the interactive corpus characteristic plot).
Words that were strongly indicative of being from the Activity Video condition include \enquote{give}, \enquote{big}, \enquote{small}, \enquote{ribbit}, \enquote{thank}, \enquote{have}, and \enquote{bus}, while words that were most characteristic of the No Video condition include \enquote{shake}, \enquote{ready}, \enquote{oh}, \enquote{on}, \enquote{going}, \enquote{going}, \enquote{see}, \enquote{let}, and the child's name.

@@

Experiment 1 found that parents who watched an activity video made more bids for joint attention and spoke more words tokens per minute to their children, but had lower lexical diversity compared to parents who played with their children as they normally would at home.
Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
Experiment 2 focuses on replicating the key findings using a stronger control group, as well as a restricted number of preregistered predictions.\footnote{Preregistration: {[}XXXX{]} }

@@

\hypertarget{participants-1}{%
\subsubsection{Participants}\label{participants-1}}
